Design and Implementation of Safe and Private Forward-Trading Platform for\\ IoT-Based Transactive Microgrids

### 2018-07-13 docs/papers/iotdi2018/feeder.tex
update

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
  font=\footnotesize,
  width=\columnwidth,
  height=0.61\columnwidth,
  ymin=-1,
 legend columns=3, 
  legend style={font=\fontsize{5}{6}\selectfont,cells={align=left},text width=4.3em,text height=1.5ex,text depth=.5ex,row sep=0.1em},
  ymax=220,
grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
  xmin=-1,
  xmax=97,
  legend pos=north west,
  xlabel=Time,
  ylabel={[kWh]},
  ytick={0, 50, 100, 150, 200},
  xtick={0, 16, 32, 48, 64, 80, 95},
  xticklabels={0:00, 4:00, 8:00, 12:00, 16:00,  20:00, 23:45},
]
\addplot[no markers, solid, greenline, semithick] table[x expr=\coordindex, y=WithoutBattery,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
\addlegendentry{Total energy traded (Test A)};
\addplot[no markers, solid, blackLine, semithick] table[x expr=\coordindex, y=WithBattery5,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
\addlegendentry{Total energy traded (Test C)};
\addplot[no markers, solid, goldLine, semithick] table[x expr=\coordindex, y=WithBattery12,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
\addlegendentry{Total energy traded (Test D)};
\addplot[no markers, solid, blueLine, semithick] table[x expr=\coordindex, y=TotalProduction, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
\addlegendentry{Total production};
\addplot[no markers, solid, redLine, semithick] table[x expr=\coordindex, y=TotalConsumption, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
\addlegendentry{Total consumption};
\end{axis}
\end{tikzpicture}
\caption{Load profile (i.e., total consumption) and generation profile (i.e., total production) in kWh per 15 minute interval aggregated across the microgrid.  The graph also shows the energy traded per interval without battery (Test A),  and with battery Tests C and D (see Table \ref{table:test-parameters}). Note that the amount of energy traded can be lower than both demand and supply at the same time because of safety constraints, which limit the amount of energy that can flow out of the producers' feeders.}
\label{fig:profile}
% \vspace{-0.2in}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
  font=\footnotesize,
  width=\columnwidth,
  height=0.61\columnwidth,
  ymin=-1,
 legend columns=3, 
  legend style={font=\fontsize{5}{6}\selectfont,cells={align=left},text width=4.3em,text height=1.5ex,text depth=.5ex,row sep=0.1em},
  ymax=220,
grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
  xmin=-1,
  xmax=97,
  legend pos=north west,
  xlabel=Time,
  ylabel={[kWh]},
  ytick={0, 50, 100, 150, 200},
  xtick={0, 16, 32, 48, 64, 80, 95},
  xticklabels={0:00, 4:00, 8:00, 12:00, 16:00,  20:00, 23:45},
]
%\addplot[no markers, solid, greenline, semithick] table[x expr=\coordindex, y=WithoutBattery,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
%\addlegendentry{Total energy traded (Test A)};
%\addplot[no markers, solid, blackLine, semithick] table[x expr=\coordindex, y=WithBattery5,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
%\addlegendentry{Total energy traded (Test C)};
%\addplot[no markers, solid, goldLine, semithick] table[x expr=\coordindex, y=WithBattery12,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
%\addlegendentry{Total energy traded (Test D)};
\addplot[no markers, solid, blueLine, semithick] table[x expr=\coordindex, y=TotalProduction, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
\addlegendentry{Total production};
\addplot[no markers, solid, redLine, semithick] table[x expr=\coordindex, y=TotalConsumption, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
\addlegendentry{Total consumption};
\end{axis}
\end{tikzpicture}
\caption{Load profile (i.e., total consumption) and generation profile (i.e., total production) in kWh per 15 minute interval aggregated across the microgrid.  The graph also shows the energy traded per interval without battery (Test A),  and with battery Tests C and D (see Table \ref{table:test-parameters}). Note that the amount of energy traded can be lower than both demand and supply at the same time because of safety constraints, which limit the amount of energy that can flow out of the producers' feeders.}
\label{fig:profile}
% \vspace{-0.2in}
\end{figure}
